Paper Title*\\ {\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and should not be used} \thanks{Identify applicable funding agency here. If none, delete this.}

### 2019-05-07 icdm/submission/includes/contribution.tex
conclusion contribution

This algorithm provides a way to compute the loss, to make the implementation successful, one still needs to access the context-pairs. The process of doing so is described in the next paragraph.

>>>>

This finishes the description of our batched approach. The next section will describe our experimental setting and the possibilities that exists to evaluate the quality of word embeddings.
